MFCCs, Chroma Features, and Spectrogram Images for Deepfake Audio Classification Using Machine Learning

### 2024-12-04 paper/paper.tex
added a couple more headers
added figures for real and fake waveforms and spectrograms

\subsection{Mel-Spectrogram Images}
Nora TODO
\subsection{Convolutional Neural Networks}
Nora TODO
\subsubsection{VGG16}
Nora TODO
\subsubsection{ResNet50}
Nora TODO

@@

@@

>>>>

\subsection{Mel-Spectrogram Images}
A Mel-Spectrogram image is an alternative method for visually representing sound. Generally, we see sound visualized as a two-dimensional waveform showing amplitude over time. Similar to MFCCs, Mel-Spectrograms are generated by performing a number of transformations on an audio sample, then representing the results as a graph.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/real_waveform.png}
  \caption{Waveform representation of a Real Audio Sample.}
  \label{fig:real_waveform}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/fake_waveform.png}
  \caption{Waveform representation of a Fake Audio Sample.}
  \label{fig:fake_waveform}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/real_spectrogram.png}
  \caption{Spectrogram representation of a Real Audio Sample.}
  \label{fig:real_spectrogram}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/fake_spectrogram.png}
  \caption{Spectrogram representation of a Fake Audio Sample.}
  \label{fig:real_spectrogram}
\end{figure}

\subsection{Convolutional Neural Networks}
Nora TODO
\subsubsection{VGG16}
Nora TODO
\subsubsection{ResNet50}
Nora TODO

\subsection{Support Vector Machine (SVM)}

@@

\subsection{Gradient Boosting}

@@

\subsection{Probably a section about the data here would be good}
